%-------------------------
% ATS-Optimized Resume for Joffre du Preez
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeAwardHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Joffre du Preez} \\ \vspace{5pt}
    \small (289) 707-1301 $|$ \href{mailto:joffre@joffredupreez.com}{\underline{joffre@joffredupreez.com}}
\end{center}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages:} Java, Python, C, PHP, JavaScript (ES6+), HTML5, CSS3, SQL \\
    \textbf{Frameworks/Libraries:} Spring Boot, React, Project Reactor, JUnit, Mockito \\
    \textbf{Tools/Platforms:} Git, Docker (containerization), Jira, IntelliJ, Visual Studio Code, Swagger (OpenAPI), GitHub Actions, Jenkins \\
    \textbf{Cloud:} AWS (Foundations), REST API design, Microservices architecture \\
    \textbf{Methodologies:} Agile/Scrum, Test-Driven Development (TDD), CI/CD pipelines
  }}
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of Guelph}{Guelph, Ontario}
    {\textbf{BCOMP Bachelor of Computing, Computer Science (Co-op)}}{Sept 2020 – Apr 2025}
  \begin{itemize}
    \item Graduated with Distinction (80\%+, ~3.7/4.0 GPA)
  \end{itemize}
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Professional Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {NCR Voyix}{Waterloo, ON}
    {Intern Software Developer}{Jan 2024 – Aug 2024}
    \resumeItemListStart
      \resumeItem{Enhanced proprietary programming language execution by optimizing runtime performance and implementing multi-threaded features.}
      \resumeItem{Developed asynchronous execution using Project Reactor to improve scalability in concurrent applications.}
      \resumeItem{Built automated performance testing tools with mocks and test suites to validate system efficiency and scalability.}
      \resumeItem{Collaborated in Agile sprints, contributing to code reviews, CI/CD workflows, and documentation.}
    \resumeItemListEnd

  \resumeSubheading
    {Tulip Retail}{Kitchener, ON}
    {Intern Software Developer}{May 2023 – Aug 2023}
    \resumeItemListStart
      \resumeItem{Extended and optimized RESTful API endpoints for an omnichannel checkout system, enabling seamless backend integration and data flow.}
      \resumeItem{Debugged high-priority client issues, optimized error logging, and implemented bug fixes to ensure platform reliability.}
      \resumeItem{Collaborated in an Agile environment, participating in sprint planning, code reviews, and release cycles.}
    \resumeItemListEnd

  \resumeSubheading
    {Exiger}{Toronto, ON}
    {Intern Software Developer}{May 2022 – Dec 2022}
    \resumeItemListStart
      \resumeItem{Automated API documentation for 123 endpoints using Swagger (OpenAPI), improving developer onboarding and integration speed.}
      \resumeItem{Integrated HashiCorp Vault for secure credential management, reducing risk of key exposure.}
      \resumeItem{Implemented proxy-based IP rotation strategies for web data scraping to improve system reliability.}
    \resumeItemListEnd

  \resumeSubheading
    {Mortgage Allies}{Remote}
    {Intern Software Developer}{May 2021 – Aug 2021}
    \resumeItemListStart
      \resumeItem{Built a full-stack mortgage planning calculator using PHP, JavaScript, and MySQL, converting Excel-based calculations into dynamic backend logic.}
      \resumeItem{Collaborated on UI development and validation for a dynamic, client-facing web application.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading{\textbf{Smart Meeting Summarizer (In Progress)}}{}
  \resumeItemListStart
    \resumeItem{Developing a full-stack platform with Spring Boot (Java) + PostgreSQL backend, JWT-secured REST APIs, and file processing for meeting and lecture uploads.}
    \resumeItem{Integrating Python NLP microservices (OpenAI Whisper, Hugging Face) for automated transcription, summarization, and task extraction.}
    \resumeItem{Building a React frontend with planned RabbitMQ/Kafka-based job queues for scalable asynchronous processing.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------AWARDS-----------
\section{Awards}
\resumeSubHeadingListStart
  \resumeAwardHeading{Hack the Job Hackathon – 2nd Place Overall}{Jan 2022}
  \resumeItemListStart
    \resumeItem{Developed a full-stack web app for dynamic personalized websites, placing 2nd overall among 30+ teams.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
